%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Technical Leader} % Job title
    {LATAM Airlines} % Organization
    {Santiago, Chile} % Location
    {Aug. 2020 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Technical Lead of the Advanced Analytics, high performance team within the company and recognized in the region. }
        \item {Scale the team from 9 to 45 members through the worst crisis in the area industry.}
        \item {In charge of the vision and management of the entire MLOps journey, allowing the operation of more than 40 data products that generate more than 110M USD per year.}
        \item {On charge of boosting and empowering the team, achieving the acquisition of tools for a budget of more than 1.5M USD and establishing strong partnerships with world leaders in MLOps (\href{https://youtu.be/kagDKNto1c4}{reference video}).}
        \item {Co-lead the process of exporting the recruitment model, for the entire VP (900+ people).}
        \item {In charge of designing and implementing the first version of the company's Trainees program. Allowing to inject trained talent with the key skills that the VP needs.}
      	\item {Recognized as Service Leader 2021. The most relevant recognition of the company and given to the 400 people who best represent the spirit and vocation of the entire company.}
      \end{cvitems}
    }

  \cventry
    {Machine Learning Engineer} % Job title
    {} % Organization
    {} % Location
    {Jun. 2019 - Aug. 2020} % Date(s)
    {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Develop the first architecture that allows training, exposing and maintaining ML models using MLOps pipelines. Accelerating data scientist workflow by approx. 80\%.}
      \item {Desing an architecture to ingest data from the sensors of the entire fleet. Almost 30 TB per day.}
      \item {Design and implement integrations between machine learning models and the company's marketing platforms increasing time to market from weeks to minutes.}
      \item {Technical leadership in the cloud resource efficiency plan, implementing FinOps practices and enabling the company to save from 2.2MM USD annually.}
    \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Engineer} % Job title
    {Xmartlab} % Organization
    {Santiago, Chile} % Location
    {May. 2018 - Dec. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and implement a large-scale data extraction mechanism. Making the main pipeline speed 15 times faster.}
        \item {Design and implement a storage architecture for 8+ heterogeneous and unstructured data products.}
      \end{cvitems}
    }

%---------------------------------------------------------
\cventry
  {Content Creator} % Job title
  {Academia Desafío LATAM} % Organization
  {Santiago, Chile} % Location
  {Sep. 2018 - May. 2019} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Develop the content of the Big Data module, covering identification of Big Data problems according to their characteristics, choose the appropriate strategies and technologies to process the data depending on its volume using tools such as Hadoop or Spark.}
    \end{cvitems}
  }

%---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {Smartbots} % Organization
    {Santiago, Chile} % Location
    {May. 2017 - May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Promote the different lines of business based on the data. These lines mainly corresponded to retail and banking. Participation in:}
      	\begin{itemize}
        	\item{Product recommendation and characterization of customers for retail.}
        	\item{Identification of the main intentions within thousands of conversations in different sources of information.}
        	\item{Construction of metrics and visualizations to measure performance, seasonality of bots use.}
      	\end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Ticblue} % Organization
    {Santiago, Chile} % Location
    {Jul. 2015 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and implementation of software components using back-end technologies (mainly Ensemble by InterSystems and JAVA EE) for integration mainly.}
        \item {Administration and exploitation of high performance database engine.}
        \item {Exploiting the transaction messaging of the ESB using BI tools.}
        \item {Integration between services of institutions (Registro Civil, Ministerio de Desarrollo Social and JUNJI) for the application process of postulants.}
        \item {Automation of information replacement activities, for remuneration payments of a government entity with more than 30,000 employees.}
        \item {Build Concepts Tests (POC) to support sales processes about real problems of potential clients.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
