%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Personal Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software and Data Engineer} % Role
    {Improving Santiago's Public Transport Metrics} % Event
    {Santiago, Chile} % Location
    {May. 2018 - Jun 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {All about data collection; Transactions of BIP cards, alerts and positions of buses. This data is collected using different mechanisms, such as web scraping and calls to APIs in a concurrent and scalable way. The data is processed and stored efficiently. Every day increases the dataset around 8GBs. The data extraction was statistically adjusted to obtain as much data as possible at different times.}
        \item {Generate metrics and visualizations efficiently, processing more than 600GBs.}
	    \item {Generate alternatives to existing routes, depending on the variant demand. Not finished.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software and Data Engineer} % Role
    {Building a clusters of similar people on Twitter} % Event
    {Santiago, Chile} % Location
    {Oct. 2017 - Dic 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)
		\item {Extract and store data efficiently.}
        \item {Prepare and clean data. Process more than 1.5 TB of text data in a distributed way.}
        \item {Build clusters of similar people.}
      \end{cvitems}
    }
\end{cventries}
