%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Research Teaching Assistant} % Job title
    {Universidad Andrés Bello} % Organization
    {Santiago, Chile} % Location
    {Oct. 2014 - Dic. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Combinatorial Optimization in Engineering:}
      		\begin{itemize}
      			\item {Preparation of a tool that performs vehicle routing in case of catastrophes for multiple customers and deposits, known as MVRPH (heuristic multi-vehicle routing problem). \href{http://revistas.ustabuca.edu.co/index.php/ITECKNE/article/view/1631}{\textbf{Paper link.}}}
      			\item {Collaboration with professors Gustavo Gatica, PhD., And Carlos Contreras, PhD. (C), in the preparation of a scientific article that proposes a solution for the Travelling Salesman Problem with a specific variant, using a multi-operator genetic algorithm as a solution.}
      		\end{itemize}
      	\item {Artificial Intelligence Search:}
      	\begin{itemize}
      		\item {Collaboration with Professor Carlos Hernández PhD, in the preparation of a scientific article that proposes a new mechanism in the detection of areas of complexity for videogame maps used in search of Artificial Intelligence problems.}
      	\end{itemize}
      	\item {Model-Driven Development:}
      	\begin{itemize}
      		\item {Collaboration with Professor Giovanni Giachetti PhD, in a systematic review of the literature.}
      	\end{itemize}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}